Publisher League Global

### 2019-09-09 analysis/001_kb_rp_pretest.Rmd
rmd reports render

```{r setup, echo = FALSE}
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "~/ojdbc8.jar")
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    Sys.getenv("kb_user"),
    Sys.getenv("kb_pwd")
  ) 
```

>>>>

```{r setup, echo = FALSE}
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "../inst/jdbc_driver/ojdbc8.jar")
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    Sys.getenv("kb_user"),
    Sys.getenv("kb_pwd")
  ) 
```

### 2019-09-09 analysis/002_kb_rp_coverage.Rmd
rmd reports render

```{r setup, echo = FALSE}
# deal with rJava memory allocation 
# https://stackoverflow.com/questions/34624002/r-error-java-lang-outofmemoryerror-java-heap-space
options(java.parameters = "-Xmx1024m")
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "~/ojdbc8.jar")
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    Sys.getenv("kb_user"),
    Sys.getenv("kb_pwd")
  ) 
```

@@

- Database: wos_b_2019
- Document Types: Articles and Reviews
- Database Collections: `WOS.SCI`, `WOS.SSCI`, `WOS.AHCI`
- Publication Period 2014 - 2017

@@

```{r}
tp_au_count <- rp_au %>% 
  mutate(N_AU = fct_other(factor(N_AU), keep = c("1", "2", "3", "4", "5"),
                          other_level = "> 5")) %>% 
  group_by(N_AU, PUBYEAR) %>% 
  summarize(N = n()) %>% 
  ungroup() %>% 
  group_by(PUBYEAR) %>% 
  mutate(PROP = N / sum(N))
tp_au_count %>%
  ggplot(aes(N_AU, PROP, fill = factor(PUBYEAR))) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  facet_grid( ~ factor(PUBYEAR)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L)) +
  labs(
    x = "Number of reprint authors per record",
    y = "Proportion",
    title = "Number of reprint authors per Web of Science record",
    subtitle = "Articles and reviews 2014 - 2018"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank())
```

@@

```{r}
rp_country_au_df %>%
  ggplot(aes(
    x = factor(COUNTRY_PER_AUTH_CNT),
    PROP,
    fill = factor(PUBYEAR)
  )) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  facet_grid( ~ PUBYEAR) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L)) +
  labs(
    x = "Number of Countries",
    y = "Proportion",
    title = "Country affiliations per reprint author",
    caption = "Derived from wos_b_2019.D_ITEMS_AUTHORS_INSTITUTIONS.COUNTRY_PER_AUTH_CNT"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank())
```

>>>>

```{r setup, echo = FALSE}
# deal with rJava memory allocation 
# https://stackoverflow.com/questions/34624002/r-error-java-lang-outofmemoryerror-java-heap-space
options(java.parameters = "-Xmx1024m")
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "../inst/jdbc_driver/ojdbc8.jar")
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    Sys.getenv("kb_user"),
    Sys.getenv("kb_pwd")
  ) 
```

@@

- Database: wos_b_2019
- Document Types: Articles and Reviews
- Database Collections: `WOS.SCI`, `WOS.SSCI`, `WOS.AHCI`
- Publication Period 2014 - 2018

@@

```{r ca_author_count}
tp_au_count <- rp_au %>% 
  mutate(N_AU = fct_other(factor(N_AU), keep = c("1", "2", "3", "4", "5"),
                          other_level = "> 5")) %>% 
  group_by(N_AU, PUBYEAR) %>% 
  summarize(N = n()) %>% 
  ungroup() %>% 
  group_by(PUBYEAR) %>% 
  mutate(PROP = N / sum(N))
tp_au_count %>%
  ggplot(aes(N_AU, PROP, fill = factor(PUBYEAR))) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  facet_grid( ~ factor(PUBYEAR)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L)) +
  labs(
    x = "Number of reprint authors per record",
    y = "Proportion",
    title = "Number of reprint authors per Web of Science record",
    subtitle = "Articles and reviews 2014 - 2018"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank())
```

@@

```{r ca_country_count}
rp_country_au_df %>%
  ggplot(aes(
    x = factor(COUNTRY_PER_AUTH_CNT),
    PROP,
    fill = factor(PUBYEAR)
  )) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  facet_grid( ~ PUBYEAR) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L)) +
  labs(
    x = "Number of Countries",
    y = "Proportion",
    title = "Country affiliations per reprint author",
    caption = "Derived from wos_b_2019.D_ITEMS_AUTHORS_INSTITUTIONS.COUNTRY_PER_AUTH_CNT"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
  theme(plot.margin = margin(30, 30, 30, 30)) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank())
```

### 2019-09-09 analysis/003_kb_fetch_ca.Rmd
rmd reports render

---
title: "Fetching Reprint Author info - v2"
output: github_document
---

@@

rmarkdown::render("kb_fetch_new.Rmd")
```

@@

```{r}
# deal with rJava memory allocation 
# https://stackoverflow.com/questions/34624002/r-error-java-lang-outofmemoryerror-java-heap-space
options(java.parameters = "-Xmx1024m")
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "~/ojdbc8.jar")
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    Sys.getenv("kb_user"),
    Sys.getenv("kb_pwd")
  ) 
```

@@

```{r}
# dump
write_csv(rp_country, "data/rp_data_14_18.csv")
```

@@

```{r}
cr_journals <- readr::read_csv("data/cr_wos.csv") %>%
  # merge springer nature brands
  mutate(publisher = ifelse(grepl("Springer", publisher, fixed = FALSE), "Springer Nature", publisher))
rp_country <- readr::read_csv("data/rp_data_14_18.csv")
issn_l <- readr::read_tsv("data/20190818.ISSN-to-ISSN-L.txt") %>%
  # manual fix Journal - American Water Works 
  add_row(ISSN = "2164-4535", `ISSN-L` = "0003-150X")
rp_df <- rp_country %>%
  left_join(issn_l, by = "ISSN") %>%
  left_join(cr_journals, by = c(`ISSN-L`= "issn_l")) %>%
  select(-issn) %>%
  distinct()
```

@@

```{r}
rp_df_oa %>%
  select(
    issn_wos = ISSN,
    country_code = INST_COUNTRYCODE,
    publication_year = PUBYEAR,
    articles = PUBS,
    journal_title, publisher, oa_journal,
    issn_l = `ISSN-L`) %>%
  write_csv("data/rp_jn_14_18.csv")
```

@@

```{r}
require(writexl)
rp_df <- readr::read_csv("data/rp_jn_14_18.csv")
tmp <- map(2014:2018, function(x) {
  rp_df %>% 
    filter(publication_year == x)
  }
)
# names
names(tmp) <- paste0("pubyear_", 2014:2018)
write_xlsx(tmp, "data/rp_14_18.xlsx")
```

>>>>

---
title: "Fetching Reprint Author information from the Web of Science"
output: github_document
---

@@

rmarkdown::render("003_kb_fetch_ca.Rmd")
```

@@

```{r}
# deal with rJava memory allocation 
# https://stackoverflow.com/questions/34624002/r-error-java-lang-outofmemoryerror-java-heap-space
options(java.parameters = "-Xmx1024m")
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "../inst/jdbc_driver/ojdbc8.jar")
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    Sys.getenv("kb_user"),
    Sys.getenv("kb_pwd")
  ) 
```

@@

```{r}
# dump
write_csv(rp_country, "../data/rp_data_14_18.csv")
```

@@

```{r}
cr_journals <- readr::read_csv("../data/cr_wos.csv") %>%
  # merge springer nature brands
  mutate(publisher = ifelse(grepl("Springer", publisher, fixed = FALSE), "Springer Nature", publisher))
rp_country <- readr::read_csv("../data/rp_data_14_18.csv")
issn_l <- readr::read_tsv("../data/20190818.ISSN-to-ISSN-L.txt") %>%
  # manual fix Journal - American Water Works 
  add_row(ISSN = "2164-4535", `ISSN-L` = "0003-150X")
rp_df <- rp_country %>%
  left_join(issn_l, by = "ISSN") %>%
  left_join(cr_journals, by = c(`ISSN-L`= "issn_l")) %>%
  select(-issn) %>%
  distinct()
```

@@

```{r}
rp_df_oa %>%
  select(
    issn_wos = ISSN,
    country_code = INST_COUNTRYCODE,
    publication_year = PUBYEAR,
    articles = PUBS,
    journal_title, publisher, oa_journal,
    issn_l = `ISSN-L`) %>%
  write_csv("../data/rp_jn_14_18.csv")
```

@@

```{r}
require(writexl)
rp_df <- readr::read_csv("../data/rp_jn_14_18.csv")
tmp <- map(2014:2018, function(x) {
  rp_df %>% 
    filter(publication_year == x)
  }
)
# names
names(tmp) <- paste0("pubyear_", 2014:2018)
write_xlsx(tmp, "../data/rp_14_18.xlsx")
```

### 2019-09-09 analysis/004_kb_fetch_publisher.Rmd
rmd reports render

---
title: "Publisher League Global"
author: "Najko Jahn"
date: "9/5/2019"
output: github_document
---

@@

```r
require(rmarkdown)
require(tidyverse)
require(RJDBC)
require(rJava)
require(writexl)
rmarkdown::render("kb_fetch_publisher_global.Rmd")
```

@@

```{r}
# deal with rJava memory allocation 
# https://stackoverflow.com/questions/34624002/r-error-java-lang-outofmemoryerror-java-heap-space
options(java.parameters = "-Xmx1024m")
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "~/ojdbc8.jar") # you may need to change the path to your db driver
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    # login credentials are stored in the .Rprofile file 
    Sys.getenv("kb_user"), 
    Sys.getenv("kb_pwd")
  ) 
```

@@

```{r}
head(rp_publisher) %>%
  knitr::kable()
# dump
write_csv(rp_publisher, "data/publisher_league_14_18.csv")
```

@@

```{r}
cr_journals <- readr::read_csv("data/cr_wos.csv") %>%
  # merge springer nature brands
  mutate(publisher = ifelse(grepl("Springer", publisher, fixed = FALSE), "Springer Nature", publisher))
rp_publisher <- readr::read_csv("data/publisher_league_14_18.csv")
issn_l <- readr::read_tsv("data/20190818.ISSN-to-ISSN-L.txt") %>%
  # manual fix Journal - American Water Works 
  add_row(ISSN = "2164-4535", `ISSN-L` = "0003-150X")
rp_df <- rp_publisher %>%
  left_join(issn_l, by = "ISSN") %>%
  left_join(cr_journals, by = c(`ISSN-L`= "issn_l")) %>%
  select(-issn) %>%
  distinct()
```

@@

```{r}
rp_df_oa %>%
  select(
    issn_wos = ISSN,
    publication_year = PUBYEAR,
    articles = PUBS,
    journal_title, publisher, oa_journal,
    issn_l = `ISSN-L`
    ) %>%
  write_csv("data/publisher_14_18.csv")
```

@@

```{r}
readr::read_csv("data/publisher_14_18.csv") %>%
  writexl::write_xlsx("data/publisher_14_18.xlsx")
```

>>>>

---
title: "Publisher League Global"
output: github_document
---

@@

```r
require(rmarkdown)
require(tidyverse)
require(RJDBC)
require(rJava)
require(writexl)
rmarkdown::render("004_kb_fetch_publisher_global.Rmd")
```

@@

```{r}
# deal with rJava memory allocation 
# https://stackoverflow.com/questions/34624002/r-error-java-lang-outofmemoryerror-java-heap-space
options(java.parameters = "-Xmx1024m")
require(tidyverse)
require(RJDBC)
require(rJava)
.jinit()
jdbcDriver <-
  JDBC(driverClass = "oracle.jdbc.OracleDriver", classPath = "../inst/jdbc_driver/ojdbc8.jar") # you may need to change the path to your db driver
jdbcConnection <-
  dbConnect(
    jdbcDriver,
    "jdbc:oracle:thin:@//biblio-p-db01:1521/bibliodb01.fiz.karlsruhe",
    # login credentials are stored in the .Rprofile file 
    Sys.getenv("kb_user"), 
    Sys.getenv("kb_pwd")
  ) 
```

@@

```{r}
head(rp_publisher) %>%
  knitr::kable()
# dump
write_csv(rp_publisher, "../data/publisher_league_14_18.csv")
```

@@

```{r}
cr_journals <- readr::read_csv("../data/cr_wos.csv") %>%
  # merge springer nature brands
  mutate(publisher = ifelse(grepl("Springer", publisher, fixed = FALSE), "Springer Nature", publisher))
rp_publisher <- readr::read_csv("../data/publisher_league_14_18.csv")
issn_l <- readr::read_tsv("../data/20190818.ISSN-to-ISSN-L.txt") %>%
  # manual fix Journal - American Water Works 
  add_row(ISSN = "2164-4535", `ISSN-L` = "0003-150X")
rp_df <- rp_publisher %>%
  left_join(issn_l, by = "ISSN") %>%
  left_join(cr_journals, by = c(`ISSN-L`= "issn_l")) %>%
  select(-issn) %>%
  distinct()
```

@@

```{r}
rp_df_oa %>%
  select(
    issn_wos = ISSN,
    publication_year = PUBYEAR,
    articles = PUBS,
    journal_title, publisher, oa_journal,
    issn_l = `ISSN-L`
    ) %>%
  write_csv("../data/publisher_14_18.csv")
```

@@

```{r}
readr::read_csv("../data/publisher_14_18.csv") %>%
  writexl::write_xlsx("../data/publisher_14_18.xlsx")
```
